---
title: "R Notebook"
output: html_notebook
---
# Preloads Energy Consumption
# Housekeeping

First we set the working directory
```{r}
dir = "/home/omar/thesis-replication-package/preloads/data_analysis"
```

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
## setting working directory
opts_knit$set(root.dir = dir)
```

```{r}
setwd(dir)
```

Next we import the libraries we need.
```{r}
library(ggplot2)
library(e1071)
library(dplyr)
library(effsize)
# Import functions we created ourselves.
source("util.r")
```

# Getting the data
We load the data and then reshape it a little bit to make it easier to work with.
```{r}
monsoon_raw_data <- read.csv("../raw_data/Aggregated_Results_Monsoon.csv")
plt_raw_data <- read.csv("../raw_data/http_post_request_payloads.txt")

combined_data <- combine_and_reshape_dataframes(monsoon_raw_data, plt_raw_data, "noremovepreload")
intact = combined_data[1:200,]
removed = combined_data[201:400,]
print(combined_data)
print(intact)
print(removed)
```

# Data Exploration

First lets get some summaries of the data..
```{r}
print("All")
summary(combined_data$energy_joules)
sd(combined_data$energy_joules)
print("Intact")
summary(intact$energy_joules)
sd(intact$energy_joules)
print("Removed")
summary(removed$energy_joules)
sd(removed$energy_joules)
```
Then we make a boxplot of the data.
```{r}
ggplot(combined_data, aes(x=treatment, y=energy_joules)) + 
  geom_boxplot() + labs(
            
              x = "Treatment", y = "Energy consumption (J)") + scale_x_discrete(labels=c("Intact", "Removed"))
ggsave("/home/omar/thesis-replication-package/preloads/data_analysis/plots/box_plot_preloads_energy_consumption.pdf")
```
We can see that the data lies very close together.


Lets inspect the 6 outliers..
```{r}
outliers <- boxplot.stats(combined_data$energy_joules)$out
out_ind <- which(combined_data$energy_joules %in% c(outliers))
outliers <- combined_data[out_ind,]
print(outliers)
outliers %>% group_by(subject, treatment) %>% summarise(Count=n())
```
We see that most of the outliers are all for the same mobile web apps (30/33 outliers) so we decide to not remove them. This is also to be expected as each mobile web app differs from the others in terms of size, logic etc.

# Testing for normality
The paired t-test assumes that the differences between pairs are normally distributed. Lets investigate..
```{r}
differences <- NULL
differences$subject <- intact$subject
differences$diff <-  removed$energy_joules - intact$energy_joules
differences <- data.frame(differences$subject, differences$diff)
differences <- differences %>%
  rename(
   subject = "differences.subject",
    diff = differences.diff
    )
print(differences)
summary(differences$diff)
stripchart(differences$diff)
boxplot(differences$diff)
```
We can see that both the median and the mean lie pretty close together. Although we have a slight skew (positively) to the right (mean is larger than median). The average and mean both circle around 0, so no big differences.

Might be interesting to look at the outliers. As we can see the majority of these outliers are,all from a positive difference between pairs so the energy consumption of MWA was higher when the preloads were removed versus when preloads were left intact.

```{r}
outliers <- boxplot.stats(differences$diff)$out
out_ind <- which(differences$diff %in% c(outliers))
differences[out_ind,]
```


Lets check whether the data is normally distributed. The QQ-plot indicates that the data is not normally distributed. To confirm we apply he Shapiro-Wilk test which returns a p-value of  2.2e-16 meaning that the hypothesis that the data comes from a normal distribution is rejected. 

```{r}
pdf(file="/home/omar/thesis-replication-package/preloads/data_analysis/plots/qqplot_preloads_energy.pdf")
differences <- removed$energy_joules - intact$energy_joules
qqnorm(differences, main="", xlab = "Normal theoretical quantile", ylab="Energy consumption differences sample quantile (J)")
qqline(differences)
dev.off()
```

```{r}
transform_and_test(removed$energy_joules, intact$energy_joules)
```
Since the differences are not normally distributed we apply several transformations to see if we can approach a normal distribution.

```{r}
transform_and_test(removed$energy_joules, intact$energy_joules, "log")
transform_and_test(removed$energy_joules, intact$energy_joules, "sqrt")
transform_and_test(removed$energy_joules, intact$energy_joules, "recip")
```

We can see that for all three transformations the data is not normally distributed.

# Hypothesis Testing
Since the data is not normally distributed we  will use the Wilcoxon signed rank test:
```{r}
wilcox.test(removed$energy_joules, intact$energy_joules, paired=TRUE)
```
As we can see this tests gives a p-value of 0.1582 which is above our 0.05 treshold and thus we cannot reject the null hypothesis. So we are not able to claim that there is a significant difference in energy consumption between MWP that use resource preloading or not.

# Effect Size Estimation
```{r}
cliffs_delta_energy <- cliff.delta(removed$energy_joules, intact$energy_joules)
print(cliffs_delta_energy)
```
As expected the value of the Cliff's delta measure is negligible.





